Community-based marine reserves produce biological and economic benefits

### 2018-01-26 Frontiers_Manuscript/Villasenor-Derbez.Rmd
Started streamlining analyses in the general manuscript

source(file = "../Scripts/robust_se.R")
source(file = "../Scripts/abundance_model.R")
```

@@

```{r load_data}
fish <- read.csv("../Data/fish_data.csv", strip.white = T, stringsAsFactors = F) %>% 
  filter(Comunidad %in% c("Isla Natividad", "Maria Elena", "Punta Herrero")) %>% 
  filter(!is.na(RC),
         !RC %in% c("Punta Prieta - La Guanera", "El Gallinero - El Ganillero (Control)"))

@@

```{r model_fit}
fish_abundance_model <- abundance_model(fish_complete)

invert_abundance_model <- abundance_model(invert_complete)
```

@@

@@

fish_model2 <- invert_complete %>% 
  filter(Comunidad == "Isla Natividad") %>% 
  mutate(Ano = as.factor(Ano)) %>% 
  group_by(RC, Ano, Sitio, Zona, Transecto) %>% 
  summarize(Abundancia = sum(Abundancia)) %>% 
  ungroup() %>% 
  glm(Abundancia ~ Ano * Zona, data = ., family = "quasipoisson")

tidy_terms <-  fish_model2 %>% 
  robust_se() %>%
  filter(grepl("Ano20.*:ZonaReserva", term)) %$%
  str_split(term, pattern = ":", simplify = T) %>% 
  as.tibble() %>% 
  set_colnames(c("Ano", "Zona")) %>% 
  select(-Zona) %>% 
  mutate(Ano = as.numeric(gsub(Ano, pattern = "Ano", replacement = "")))

robust_se(fish_model2) %>%
  filter(grepl("Ano20.*:ZonaReserva", term)) %>% 
  cbind(tidy_terms) %>%
  mutate(p = ifelse(p.value < 0.05, "p < 0.05", "p > 0.05")) %>% 
  ggplot(aes(x = Ano, y = estimate)) +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0, color = "red", size = 1) +
  geom_point(aes(fill = p), size = 4, shape = 21, color = "black") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_classic() +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  theme(legend.justification = c(0, 0), 
        legend.position = c(0.55, 0.01))

>>>>

source(file = "../Scripts/robust_se.R")
source(file = "../Scripts/model.R")
source(file = "../Scripts/plot_model.R")
```

@@

```{r load_data}
fish <- read.csv("../Data/fish_data.csv", strip.white = T, stringsAsFactors = F) %>% 
  filter(Comunidad %in% c("Isla Natividad", "Maria Elena", "Punta Herrero")) %>% 
  filter(!is.na(RC),
         !RC %in% c("Punta Prieta - La Guanera", "El Gallinero - El Ganillero (Control)", "El Faro - El Faro (Control)", "Anegado de Chal - Anegado de Chal (Control)"))

@@

```{r model_fit}
fish_abundance_model <- fish_complete %>% 
  mutate(Ano = as.factor(Ano)) %>% 
  group_by(Comunidad, RC, Ano, Sitio, Zona, Transecto) %>% 
  summarize(Abundancia = sum(Abundancia)) %>% 
  model(com = "Isla Natividad", sfe = F, family = "quasipoisson")

# invert_abundance_model <- abundance_model(invert_complete)
```

@@

```{r}
fish_complete %>% 
  group_by(Comunidad, RC, Ano, Sitio, Zona, Transecto) %>% 
  summarize(Abundancia = sum(Abundancia)) %>%
  filter(Comunidad == "Punta Herrero") %>% 
  group_by(Zona, Ano) %>% 
  summarize(Abundancia = mean(Abundancia)) %>% 
  ggplot(aes(x = Ano, y = Abundancia, color = Zona)) +
  geom_point() +
  geom_line()
```

```{r}
fish_complete %>% 
  group_by(Comunidad, RC, Ano, Sitio, Zona, Transecto) %>% 
  summarize(Abundancia = sum(Abundancia)) %>%
  filter(Comunidad == "Punta Herrero") %>% 
  group_by(Zona, Ano) %>% 
  summarize(Abundancia = mean(Abundancia)) %>% 
  spread(Zona, Abundancia) %>%
  mutate(Abundancia = c(183.94, Reserva[-1] - Control[-1] - 183.94)) %>%
  ggplot(aes(x = Ano, y = Abundancia)) +
  geom_point() +
  geom_line()
```

```{r}
com <- "Maria Elena"

jc3 <- fish_complete %>% 
  mutate(Ano = as.factor(Ano)) %>% 
  group_by(Comunidad, RC, Ano, Sitio, Zona, Transecto, GeneroEspecie) %>% 
  summarize(Abundancia = sum(Abundancia)) %>% 
  filter(Comunidad == com) %>%
  lm(Abundancia ~ Ano * Zona + GeneroEspecie, data = .)

fish_complete %>% 
  mutate(Ano = as.factor(Ano)) %>% 
  group_by(Comunidad, RC, Ano, Sitio, Zona, Transecto) %>% 
  summarize(Abundancia = sum(Abundancia)) %>% 
  filter(Comunidad == com) %>%
  lm(Abundancia ~ Ano * Zona, data = .) %>% #summary()
  plot_model()

@@
